A Closed-Form Solution to the Doppler Imaging Problem

### 2021-10-02 src/ms.tex
fix color normalization and inclination

\subsection{Solution for the map}
\label{sec:solve_y}
%
Given a single rest-frame spectrum $\bvec{s}$, the model for the flux vector may be written as
%
\begin{align}
    \label{eq:inverse:fy}
    \bvec{f}
     & =
    \Doppler
    \,
    \bvec{S}
    \,
    \bvec{y}
    \quad,
\end{align}
%
where
%
\begin{align}
    \label{eq:inverse:S}
    \bvec{S} =
    \begin{pmatrix}
        \quadquad\bvec{s}\quadquad &                            &                            &                            &        \\
                                   & \quadquad\bvec{s}\quadquad &                            &                            &        \\
                                   &                            & \quadquad\bvec{s}\quadquad &                            &        \\
                                   &                            &                            & \quadquad\bvec{s}\quadquad &        \\
                                   &                            &                            &                            & \ddots
    \end{pmatrix}
\end{align}
%
is a $(NK' \times N)$ block matrix constructed by repeating the column vector $\bvec{s}$ $N$ times in blocks along the main diagonal.
%
Given prior mean $\boldsymbol{\mu}_\bvec{y}$ and covariance $\boldsymbol{\Lambda}_\bvec{y}$ on $\bvec{y}$, the MAP solution is given by
%
\begin{align}
    \label{eq:inverse:y1hat}
    \bvec{\hat{y}} & =
    \boldsymbol{\Sigma}_\mathbf{\hat{y}}
    \left(
    \bvec{S}^\top\Doppler^\top
    {\boldsymbol{\Sigma}_\mathbf{f}}^{-1}
    \bvec{f}
    +
    {\boldsymbol{\Lambda}_\bvec{y}}^{-1} \boldsymbol{\mu}_\bvec{y}
    \right)
    \quad,
\end{align}
%
with covariance
%
\begin{align}
    \label{eq:inverse:y1cov}
    \boldsymbol{\Sigma}_\bvec{\hat{y}} & =
    \left(
    \bvec{S}^\top\Doppler^\top
    {\boldsymbol{\Sigma}_\bvec{f}}^{-1}
    \Doppler\bvec{S}
    +
    {\boldsymbol{\Lambda}_\bvec{y}}^{-1}
    \right)^{-1}
    \quad.
\end{align}
%
If we choose a prior with diagonal covariance that is constant for each spherical harmonic order $m$,
%
\begin{align}
    \boldsymbol{\Lambda}_\bvec{y} & =
    \mathrm{diag} \left(
    \sigma_0^2
    \quad\quad\quad\quad
    \sigma_1^2
    \quad\quad\quad\quad
    \sigma_1^2
    \quad\quad\quad\quad
    \sigma_1^2
    \quad\quad\quad\quad
    \sigma_2^2
    \quad\quad\quad\quad
    \sigma_2^2
    \quad\quad\quad\quad
    \sigma_2^2
    \quad\quad\quad\quad
    \sigma_2^2
    \quad\quad\quad\quad
    \sigma_2^2
    \quad\quad\quad\quad
    \cdots
    \right)
    \quad,
\end{align}
%
we are in fact imposing an isotropic prior with an angular power spectrum given by $C_l = \sigma_l^2$
\citep[e.g.,][]{Baldi2006}. 
This is especially useful if the typical angular scale of features on the surface of the star is known or if a Gaussian prior can be placed on it.
Alternatively, we may compute $\boldsymbol{\Lambda}_\bvec{y}$ from the Gaussian process formalism in \citet{Luger2021b} to incorporate explicit prior information on the typical latitudes, sizes, and contrasts of spots. We discuss this point further in \S\ref{sec:discussion}.

@@

Once the MAP solution has been found for both $\bvec{s}$ and $\bvec{y}$, the covariance of one conditioned on the other can be computed from the formulae above. 
However, this is necessarily a lower bound on the true covariance of the solution, since it neglects any covariance \emph{between} $\bvec{s}$ and $\bvec{y}$. 
To \emph{correctly} account for this, one must resort to Monte Carlo methods or other sampling techniques. 
We discuss this further in \S\ref{sec:discussion}.

@@

In the following sections we discuss various approaches to solving the Doppler imaging problem for this dataset.
Unless otherwise noted, in all experiments we adopt a Gaussian prior for the spherical harmonic coefficients $\bvec{y}$ with mean $\boldsymbol{\mu}_\bvec{y} = \left(1 \quad\quad \bvec{0}\right)$ and covariance $\boldsymbol{\Lambda}_\bvec{y} = 10^{-4} \bvec{I}$, corresponding to a flat power spectrum prior.
When solving for the rest frame spectrum, we also place a Gaussian prior on $\bvec{s}$ with unit mean and covariance $\boldsymbol{\Lambda}_\bvec{s} = 10^{-3}\bvec{I}$.
These choices are arbitrary and primarily based on trial-and-error given knowledge of the true solutions. We discuss strategies for choosing optimal priors for real datasets in \S\ref{sec:discussion} below.

@@

Interestingly, while the map uncertainty still increases toward the south pole (bottom panel), its magnitude is smaller than that in Figure~\ref{fig:spot_infer_y}. This is counter-intuitive, since the continuum-normalized spectrum should contain \emph{less} information than the unnormalized one. Indeed, the uncertainties shown in the figure are conditioned on our estimate of the baseline, so they are actually a strict \emph{lower bound} on the map uncertainty.
In order to constrain the true uncertainty on the solution to this bilinear problem, we must resort to approximate sampling methods such as MCMC. 
We discuss this further in \S\ref{sec:discussion}.

@@

The problem setup is the same as that discussed in \S\ref{sec:eigen}, where our full map vector $\bvec{a}$ is the outer product of a spectral matrix $\mathbb{S}$, whose $J$ columns are the different spectral components, and a spherical harmonic coefficient matrix $\mathbb{Y}^\top$, whose $J$ rows are the corresponding coefficient vectors. 
For simplicity, in this experiment we consider only $J = 2$ map components and further require that the surface map for the second component is the complement of the surface map for the first component. Specifically, the first component map ($\bvec{y_0}$, the first row of $\mathbb{Y}^\top$) corresponds to the background photosphere, whose value is unity everywhere except within the \texttt{SPOT} feature, where the value is zero. The second component map ($\bvec{y_1}$, the second row of $\mathbb{Y}^\top$) corresponds to the spot and is zero in the photosphere and unity within the spot.
The two columns of $\mathbb{S}$ are $\bvec{s_0}$ and $\bvec{s_1}$, the unknown spectral components corresponding to the photosphere and the spot, repsectively.
%
\begin{figure}[p!]
    \begin{centering}
        \includegraphics[width=0.39\linewidth]{figures/twospec_timeseries.pdf}
        \includegraphics[width=0.59\linewidth]{figures/twospec_maps.pdf}
        \includegraphics[width=\linewidth]{figures/twospec_spectra1.pdf}
        \includegraphics[width=\linewidth]{figures/twospec_spectra2.pdf}
        \caption{%
            An example of a star whose spectrum is different within the spot and outside of the spot.
            We are able to infer both the surface map of the star (upper right) and the two component spectra (lower two panels), assuming virtually no prior knowledge of either.
            The optimization step in this experiment ran in \timeInferTwoSpec.
        }
        \label{fig:twospec}
    \end{centering}
\end{figure}
%
We set $\bvec{s_0}$ to unity everywhere, with an absorption feature at $643$~nm similar to the one in the previous experiments. The spot spectrum $\bvec{s_1}$ corresponds to two absorption lines on either side of this feature, and the baseline intensity is set to half that of the photospheric background.
%
The rest frame spectrum at any point on the surface of the star is then a linear combination of $\bvec{s_0}$ and $\bvec{s_1}$, weighted by the respective surface maps $\bvec{y_0}$ and $\bvec{y_1}$.
%
We generate the synthetic dataset in the same way as in \S\ref{sec:spot_y1}: 16 spectra, each with 70 wavelength bins observed with SNR$\sim 10^{3}$.

@@

The results are shown in the bottom panel of Figure~\ref{fig:twospec}.
Even though we assume no knowledge of the surface map---except its intensity is bounded in $[0, 1]$---we are able to recover the \spot feature just as well as in the previous experiments.
We also recover the two spectral components quite well. Our solution for the photospheric component, however, is noticeably better than that for the spot component, simply because effective SNR of the former is larger due to its greater surface area and higher baseline intensity. We also slightly overestimate the baseline level of the spot spectrum, but we correctly recover the locations, shapes, and depths of the two absorption lines. Note, importantly, that the nonlinear optimization step does not yield uncertainties (or lower bounds, like the bilinear solver); for this, we must resort to MCMC sampling (see \S\ref{sec:discussion}).

@@

Having shown that our model performs well on synthetic data, we now turn to a real dataset: the VLT/CRIRES observations of Luhman 16B (WISE 1049-5319B) presented in the Doppler imaging study of \citet{Crossfield2014}. Luhman 16B belongs to a binary brown dwarf system, which at a distance of 2 pc are the closest known brown dwarfs to the Solar system. Nevertheless, the object is intrinsically dim and, with a projected rotational velocity $v \sin i = 26.1$ km/s, is at the slow end of what can be imaged using the traditional Doppler imaging technique. Therefore, unlike those of classical Doppler imaging targets, the spectral lines of Luhman 16B do not individually show obvious spot modulation (Figure~\ref{fig:spot}) from one epoch to the next; nor are the spectral templates for these objects particularly well understood. Nonetheless, we chose to model Luhman 16B specifically to show the power behind our new methodology, in particular its ability to learn both the surface map and the rest frame spectrum simultaneously from the entire dataset---not just from unblended spectral lines that have reliable templates.

@@

\citet{Crossfield2014} then employed the common technique of Least Squares Deconvolution \citep[LSD;][]{Donati1997} to transform each of the 14 spectra in Figure~\ref{fig:luhman16b:data_model} into a single high-SNR line spanning 35 pixels, which was used as the input to their Doppler imaging code, based on that of \citet{Vogt1987}. They discretized the stellar surface using 200 cells and solved for the optimal surface map with a maximum entropy prior as in \citet{Vogt1987}, assuming a fiducial inclination $i=60^\circ$ roughly based on the photometric rotation period and the inferred value of $v\sin i$; given the low SNR of the dataset, they were unable to place meaningful constraints on $i$. We reproduce their resulting surface brightness map in the right panel of Figure~\ref{fig:luhman16b:maps}, seen at six different phases spanning a full rotation.

\begin{figure}[p!]
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/luhman16b_data_model.pdf} % 
        \caption{%
            Calibrated and tellurics-corrected CRIRES spectra of Luhman 16B from \citet{Crossfield2014} taken at 14 epochs spanning a full rotation of the brown dwarf (black points). Our maximum \emph{a posteriori} solution is shown as the orange curves.
        }
        \label{fig:luhman16b:data_model}
    \end{centering}
\end{figure}
%
\begin{figure}[p!]
    \begin{centering}
        \includegraphics[width=0.8\linewidth]{figures/luhman16b_spectra.pdf} % 
        \caption{%
            Unbroadened template spectra used to model the data in \citet{Crossfield2014} (blue curves). These were used as a prior on the spectra inferred in this work (orange curves). We infer a slightly different depth for some lines, as well as subtle changes in the continuum.
        }
        \label{fig:luhman16b:template_spectra}
    \end{centering}
\end{figure}

In our analysis, we use the same data (Figure~\ref{fig:luhman16b:data_model}) and the same spectral template (Figure~\ref{fig:luhman16b:template_spectra}), but instead following the methodology derived in this work. Our problem is similar to that in \S\ref{sec:spot_y1bs}, in which we treat both the spectrum and the surface map as unknowns given continuum-normalized spectra as input. However, this time we use the template spectrum as the prior mean on the true rest frame spectrum $\bvec{s}$, setting the prior standard deviation to one percent (i.e., a covariance $\boldsymbol{\Lambda}_\bvec{s} = 10^{-4}\bvec{I}$) to allow the model to learn any small deviations from the template. We must also change the way we model the continuum normalization (\S\ref{sec:norm}), given the high density of spectral lines and the consequent difficulty of finding a reliable continuum level to normalize against. Instead, we treat the unknown continuum normalization factor for each of the 14 epochs as a free parameter of the model, $f \sim \mathrm{Uniform}(0.3, 3.0)$; we also allow for a small, time-independent, additive offset $\Delta \sim \mathcal{N}(0, 0.1^2)$ for each of the four detectors. We assume the same fiducial inclination $i = 60^\circ$, a rotational period $P = 4.9$ days, and allow the linear limb darkening coefficient and projected velocity to vary subject to $u_1 \sim \mathrm{Uniform}(0, 1)$ and $v \sin i \sim \mathcal{N}(26.1, 0.2^2)$ km/s, respectively, as in \citet{Crossfield2014}. Finally, we place a uniform prior on the pixel intensities $\bvec{p} \sim \mathrm{Uniform}(0, 1)$ as in \S\ref{sec:twospec}, linearly transforming to an $l_\mathrm{max} = 10$ spherical harmonic representation of the map to compute the model at each step. We must therefore solve for $2 \times (l_\mathrm{max} + 1)^2 = 242$ free parameters for the pixelized surface map, $3,748$ free parameters for the rest frame spectrum across each of the four detectors (equal to the size of our template spectrum after removing outliers), $18$ parameters describing the continuum normalization, and $2$ stellar parameters (the linear limb darkening coefficient and the projected velocity). In total, our model has just over $4,000$ free parameters.

@@

The right panel of Figure~\ref{fig:luhman16b:maps} shows our principal result: the inferred solution for the surface brightness map of Luhman 16B; compare to the right panel, showing the solution inferred by \citet{Crossfield2014}. Broadly speaking, the two surface maps agree rather well: we infer the same circumpolar bright spot, of about the same size and at roughly the same phase, as in the earlier work. We also infer a similar dark feature on the ``back'' side of the object (visible near the sub-observer point at $t = 2.4$ hours). Bright equatorial regions also broadly match between both solutions. There are some important differences, such as the contrast of the dark feature seen at $t = 0.0$ hours and the behavior of the $t = 2.4$ hour dark region beyond $60^\circ$ of the visible pole. In general, we find that different choices for our priors---in particular the regularization on the pixels, the prior on the limb darkening coefficient, and the value of the inclination of the star---result in maps that differ substantially. We do, however, agree with \citet{Crossfield2014} in that the polar bright spot is the most robust of the inferred features, followed by the bottom portion of the dark spot seen at $t = 2.4$ hours. Once again, since this is simply an \emph{optimization}, we are unable to place reliable uncertainties on our solutions. These require a sampling scheme like MCMC (\S\ref{sec:discussion}).

@@

\xxx{%
    \begin{enumerate}
        %
        \item%
              Concerning our SPOT maps: a gaussian prior with unit mean is a pretty bad prior for the spectrum.
              In a more realistic scenario, we'd know a lot more information about the spectrum---such as where the lines are and some estimate of their shapes and depths---so the fidelity of our maps would be higher. This is what we did in the Luhman 16B case, and it works well.
              %
        \item%
              We are not addressing differential rotation and convective blueshift.
              These make the integral in Equation~(\ref{eq:deconv:kT}) very difficult to solve. 
              We will tackle this in the next paper.
              %
        \item%
              We are always integrating over the entire disk of the star. Can integrate over the unocculted
              disk during an occultation (should actually be pretty trivial) so this can be used for Doppler
              tomography once I have some time to work it out!
        \item%
              Telluric lines could be learned from the data as in \citet{Bedell2019}.
              %
        \item% 
              The instrumental profile is another Toeplitz matrix that can be dotted into Equation~(\ref{eq:linear:f}).
              %
        \item Discuss the case where the inclination/period/velocity is unknown, such as the case 
              with Luhman 16B.
              The problem is not linear in these variables, so we need MCMC. 
              But our model is differentiable, so we can easily use HMC. 
              Discuss.
              %
        \item%
              Discuss: how to choose priors. Can use cross-validation to choose best regularization strength. In general, a positivity prior on the pixels is preferred.
        \item%
              Luhman 16B: we didn't account for finite exposure time. We didn't properly model instrumental broadening. We didn't do MCMC. We didn't vary the inclination. We didn't use maximum entropy regularization. But we solved for a whopping 4,000 parameters in under 3 minutes. We used the full spectrum.
    \end{enumerate}
}

>>>>

\subsection{Solution for the map}
\label{sec:solve_y}
%
Given a single rest-frame spectrum $\bvec{s}$, the model for the flux vector may be written as
%
\begin{align}
    \label{eq:inverse:fy}
    \bvec{f}
     & =
    \Doppler
    \,
    \bvec{S}
    \,
    \bvec{y}
    \quad,
\end{align}
%
where
%
\begin{align}
    \label{eq:inverse:S}
    \bvec{S} =
    \begin{pmatrix}
        \quadquad\bvec{s}\quadquad &                            &                            &                            &        \\
                                   & \quadquad\bvec{s}\quadquad &                            &                            &        \\
                                   &                            & \quadquad\bvec{s}\quadquad &                            &        \\
                                   &                            &                            & \quadquad\bvec{s}\quadquad &        \\
                                   &                            &                            &                            & \ddots
    \end{pmatrix}
\end{align}
%
is a $(NK' \times N)$ block matrix constructed by repeating the column vector $\bvec{s}$ $N$ times in blocks along the main diagonal.
%
Given prior mean $\boldsymbol{\mu}_\bvec{y}$ and covariance $\boldsymbol{\Lambda}_\bvec{y}$ on $\bvec{y}$, the MAP solution is given by
%
\begin{align}
    \label{eq:inverse:y1hat}
    \bvec{\hat{y}} & =
    \boldsymbol{\Sigma}_\mathbf{\hat{y}}
    \left(
    \bvec{S}^\top\Doppler^\top
    {\boldsymbol{\Sigma}_\mathbf{f}}^{-1}
    \bvec{f}
    +
    {\boldsymbol{\Lambda}_\bvec{y}}^{-1} \boldsymbol{\mu}_\bvec{y}
    \right)
    \quad,
\end{align}
%
with covariance
%
\begin{align}
    \label{eq:inverse:y1cov}
    \boldsymbol{\Sigma}_\bvec{\hat{y}} & =
    \left(
    \bvec{S}^\top\Doppler^\top
    {\boldsymbol{\Sigma}_\bvec{f}}^{-1}
    \Doppler\bvec{S}
    +
    {\boldsymbol{\Lambda}_\bvec{y}}^{-1}
    \right)^{-1}
    \quad.
\end{align}
%
If we choose a prior with diagonal covariance that is constant for each spherical harmonic order $m$,
%
\begin{align}
    \boldsymbol{\Lambda}_\bvec{y} & =
    \mathrm{diag} \left(
    \sigma_0^2
    \quad\quad\quad\quad
    \sigma_1^2
    \quad\quad\quad\quad
    \sigma_1^2
    \quad\quad\quad\quad
    \sigma_1^2
    \quad\quad\quad\quad
    \sigma_2^2
    \quad\quad\quad\quad
    \sigma_2^2
    \quad\quad\quad\quad
    \sigma_2^2
    \quad\quad\quad\quad
    \sigma_2^2
    \quad\quad\quad\quad
    \sigma_2^2
    \quad\quad\quad\quad
    \cdots
    \right)
    \quad,
\end{align}
%
we are in fact imposing an isotropic prior with an angular power spectrum given by $C_l = \sigma_l^2$
\citep[e.g.,][]{Baldi2006}. 
This is especially useful if the typical angular scale of features on the surface of the star is known or if a Gaussian prior can be placed on it.
Alternatively, we may compute $\boldsymbol{\Lambda}_\bvec{y}$ from the Gaussian process formalism in \citet{Luger2021b} to incorporate explicit prior information on the typical latitudes, sizes, and contrasts of spots. We discuss this point further in \S\ref{sec:discussion:priors}.

@@

Once the MAP solution has been found for both $\bvec{s}$ and $\bvec{y}$, the covariance of one conditioned on the other can be computed from the formulae above. 
However, this is necessarily a lower bound on the true covariance of the solution, since it neglects any covariance \emph{between} $\bvec{s}$ and $\bvec{y}$. 
To \emph{correctly} account for this, one must resort to Monte Carlo methods or other sampling techniques. 
We discuss this further in \S\ref{sec:discussion:mcmc}.

@@

In the following sections we discuss various approaches to solving the Doppler imaging problem for this dataset.
Unless otherwise noted, in all experiments we adopt a Gaussian prior for the spherical harmonic coefficients $\bvec{y}$ with mean $\boldsymbol{\mu}_\bvec{y} = \left(1 \quad\quad \bvec{0}\right)$ and covariance $\boldsymbol{\Lambda}_\bvec{y} = 10^{-4} \bvec{I}$, corresponding to a flat power spectrum prior.
When solving for the rest frame spectrum, we also place a Gaussian prior on $\bvec{s}$ with unit mean and covariance $\boldsymbol{\Lambda}_\bvec{s} = 10^{-3}\bvec{I}$.
These choices are arbitrary and primarily based on trial-and-error given knowledge of the true solutions. We discuss strategies for choosing optimal priors for real datasets in \S\ref{sec:discussion:priors} below.

@@

Interestingly, while the map uncertainty still increases toward the south pole (bottom panel), its magnitude is smaller than that in Figure~\ref{fig:spot_infer_y}. This is counter-intuitive, since the continuum-normalized spectrum should contain \emph{less} information than the unnormalized one. Indeed, the uncertainties shown in the figure are conditioned on our estimate of the baseline, so they are actually a strict \emph{lower bound} on the map uncertainty.
In order to constrain the true uncertainty on the solution to this bilinear problem, we must resort to approximate sampling methods such as MCMC. 
We discuss this further in \S\ref{sec:discussion:mcmc}.

@@

The problem setup is the same as that discussed in \S\ref{sec:eigen}, where our full map vector $\bvec{a}$ is the outer product of a spectral matrix $\mathbb{S}$, whose $J$ columns are the different spectral components, and a spherical harmonic coefficient matrix $\mathbb{Y}^\top$, whose $J$ rows are the corresponding coefficient vectors. 
For simplicity, in this experiment we consider only $J = 2$ map components and further require that the surface map for the second component is the complement of the surface map for the first component. Specifically, the first component map ($\bvec{y_0}$, the first row of $\mathbb{Y}^\top$) corresponds to the background photosphere, whose value is unity everywhere except within the \texttt{SPOT} feature, where the value is zero. The second component map ($\bvec{y_1}$, the second row of $\mathbb{Y}^\top$) corresponds to the spot and is zero in the photosphere and unity within the spot.
The two columns of $\mathbb{S}$ are $\bvec{s_0}$ and $\bvec{s_1}$, the unknown spectral components corresponding to the photosphere and the spot, repsectively.
%
\begin{figure}[p!]
    \begin{centering}
        \includegraphics[width=0.39\linewidth]{figures/twospec_timeseries.pdf}
        \includegraphics[width=0.59\linewidth]{figures/twospec_maps.pdf}
        \includegraphics[width=\linewidth]{figures/twospec_spectra1.pdf}
        \includegraphics[width=\linewidth]{figures/twospec_spectra2.pdf}
        \caption{%
            An example of a star whose spectrum is different within the spot and outside of the spot.
            We are able to infer both the surface map of the star (upper right) and the two component spectra (lower two panels), assuming virtually no prior knowledge of either.
            The optimization step in this experiment ran in \timeInferTwoSpec.
        }
        \label{fig:twospec}
    \end{centering}
\end{figure}
%
We set $\bvec{s_0}$ to unity everywhere, with an absorption feature at $643$~nm similar to the one in the previous experiments. The spot spectrum $\bvec{s_1}$ corresponds to two absorption lines on either side of this feature, and the baseline intensity is set to half that of the photospheric background.
%
The rest frame spectrum at any point on the surface of the star is then a linear combination of $\bvec{s_0}$ and $\bvec{s_1}$, weighted by the respective surface maps $\bvec{y_0}$ and $\bvec{y_1}$.
%
We generate the synthetic dataset in the same way as in \S\ref{sec:spot_y1}: 16 spectra, each with 70 wavelength bins observed with SNR $\sim 10^{3}$.

@@

The results are shown in the bottom panel of Figure~\ref{fig:twospec}.
Even though we assume no knowledge of the surface map---except its intensity is bounded in $[0, 1]$---we are able to recover the \spot feature just as well as in the previous experiments.
We also recover the two spectral components quite well. Our solution for the photospheric component, however, is noticeably better than that for the spot component, simply because effective SNR of the former is larger due to its greater surface area and higher baseline intensity. We also slightly overestimate the baseline level of the spot spectrum, but we correctly recover the locations, shapes, and depths of the two absorption lines. Note, importantly, that the nonlinear optimization step does not yield uncertainties (or lower bounds, like the bilinear solver); for this, we must resort to MCMC sampling (see \S\ref{sec:discussion:mcmc}).

@@

Having shown that our model performs well on synthetic data, we now turn to a real dataset: the VLT/CRIRES observations of Luhman 16B (WISE 1049-5319B) presented in the Doppler imaging study of \citet{Crossfield2014}. Luhman 16B belongs to a binary brown dwarf system, which at a distance of 2 pc are the closest known brown dwarfs to the Solar system. Nevertheless, the object is intrinsically dim and, with a projected rotational velocity $v \sin i = 26.1$ km/s, is at the slow end of what can be imaged using the traditional Doppler imaging technique. Therefore, unlike those of classical Doppler imaging targets, the spectral lines of Luhman 16B do not individually show large scale spot modulation (Figure~\ref{fig:spot}) from one epoch to the next; nor are the spectral templates for these objects particularly well understood. Nonetheless, we chose to model Luhman 16B specifically to show the power behind our new methodology, in particular its ability to learn both the surface map and the rest frame spectrum simultaneously from the entire dataset---not just from unblended spectral lines that have reliable templates.

@@

\citet{Crossfield2014} then employed the common technique of Least Squares Deconvolution \citep[LSD;][]{Donati1997} to transform each of the 14 spectra in Figure~\ref{fig:luhman16b:data_model} into a single high-SNR line spanning 35 pixels, which was used as the input to their Doppler imaging code, based on that of \citet{Vogt1987}. They discretized the stellar surface using 200 cells and solved for the optimal surface map with a maximum entropy prior as in \citet{Vogt1987}, assuming a fiducial inclination $i=70^\circ$ roughly based on the photometric rotation period and the inferred value of $v\sin i$; given the low SNR of the dataset, they were unable to place meaningful constraints on $i$. We reproduce their resulting surface brightness map in the right panel of Figure~\ref{fig:luhman16b:maps}, seen at six different phases spanning a full rotation.

\begin{figure}[p!]
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/luhman16b_data_model.pdf} % 
        \caption{%
            Calibrated and tellurics-corrected CRIRES spectra of Luhman 16B from \citet{Crossfield2014} taken at 14 epochs spanning a full rotation of the brown dwarf (black points). Our maximum \emph{a posteriori} solution is shown as the orange curves.
        }
        \label{fig:luhman16b:data_model}
    \end{centering}
\end{figure}
%
\begin{figure}[p!]
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/luhman16b_spectra.pdf} % 
        \caption{%
            Unbroadened template spectra used to model the data in \citet{Crossfield2014} (blue curves). These were used as a prior on the spectra inferred in this work (orange curves). We infer a slightly different depth for some lines, as well as subtle changes in the continuum.
        }
        \label{fig:luhman16b:template_spectra}
    \end{centering}
\end{figure}

In our analysis, we use the same data (Figure~\ref{fig:luhman16b:data_model}) and the same spectral template (Figure~\ref{fig:luhman16b:template_spectra}), but instead following the methodology derived in this work. Our problem is similar to that in \S\ref{sec:spot_y1bs}, in which we treat both the spectrum and the surface map as unknowns given continuum-normalized spectra as input. However, this time we use the template spectrum as the prior mean on the true rest frame spectrum $\bvec{s}$, setting the prior standard deviation to one percent (i.e., a covariance $\boldsymbol{\Lambda}_\bvec{s} = 10^{-4}\bvec{I}$) to allow the model to learn any small deviations from the template. We must also change the way we model the continuum normalization (\S\ref{sec:norm}), given the high density of spectral lines and the consequent difficulty of finding a reliable continuum level to normalize against. Instead, we treat the unknown continuum normalization factor for each of the 14 epochs as a free parameter of the model, $f \sim \mathrm{Uniform}(0.3, 3.0)$; we also allow for a small, time-independent, additive offset $\Delta \sim \mathcal{N}(0, 0.1^2)$ for each of the four detectors. We assume the same fiducial inclination $i = 70^\circ$, a rotational period $P = 4.9$ days, and allow the linear limb darkening coefficient and projected velocity to vary subject to $u_1 \sim \mathrm{Uniform}(0, 1)$ and $v \sin i \sim \mathcal{N}(26.1, 0.2^2)$ km/s, respectively, as in \citet{Crossfield2014}. Finally, we place a uniform prior on the pixel intensities $\bvec{p} \sim \mathrm{Uniform}(0, 1)$ as in \S\ref{sec:twospec}, linearly transforming to an $l_\mathrm{max} = 10$ spherical harmonic representation of the map to compute the model at each step. We must therefore solve for $2 \times (l_\mathrm{max} + 1)^2 = 242$ free parameters for the pixelized surface map, $3,748$ free parameters for the rest frame spectrum across each of the four detectors (equal to the size of our template spectrum after removing outliers), $18$ parameters describing the continuum normalization, and $2$ stellar parameters (the linear limb darkening coefficient and the projected velocity). In total, our model has just over $4,000$ free parameters.

@@

The right panel of Figure~\ref{fig:luhman16b:maps} shows our principal result: the inferred solution for the surface brightness map of Luhman 16B; compare to the right panel, showing the solution inferred by \citet{Crossfield2014}. Broadly speaking, the two surface maps agree rather well: we infer the same circumpolar bright spot, of about the same size and at roughly the same phase, as in the earlier work. We also infer a similar dark feature on the ``back'' side of the object (visible near the sub-observer point at $t = 2.4$ hours). Bright equatorial regions also broadly match between both solutions. There are some important differences, such as the contrast of the dark feature seen at $t = 0.0$ hours and the behavior of the $t = 2.4$ hour dark region beyond $60^\circ$ of the visible pole. In general, we find that different choices for our priors---in particular the regularization on the pixels, the prior on the limb darkening coefficient, and the value of the inclination of the star---result in maps that differ substantially. We do, however, agree with \citet{Crossfield2014} in that the polar bright spot is the most robust of the inferred features, followed by the bottom portion of the dark spot seen at $t = 2.4$ hours. Once again, since this is simply an \emph{optimization}, we are unable to place reliable uncertainties on our solutions. These require a sampling scheme like MCMC (\S\ref{sec:discussion:mcmc}).

@@

\subsection{Luhman 16B}
\label{sec:discussion:luhman}

In \S\ref{sec:luhman16b} we validated our novel approach by reproducing the results of \citet{Crossfield2014}. Despite the fact that we obtained a qualitatively similar surface map for Luhman 16B (Figure~\ref{fig:luhman16b:maps}), there are several aspects to our approach that could be improved in future work. First, we did not vary the inclination, but instead kept it fixed at the fiducial value $i = 70^\circ$ used in \citet{Crossfield2014}. The authors of that study argued that the SNR of the dataset was too low to constrain the inclination, and that their surface maps did not qualitatively change by varying the inclination between $60^\circ$ and $90^\circ$, the range consistent with the joint knowledge of the rotation period and $v\sin i$. \xxx{...}

We didn't account for finite exposure time. We didn't properly model instrumental broadening. We didn't do MCMC. We didn't vary the inclination. We didn't use maximum entropy regularization. But we solved for a whopping 4,000 parameters in under 3 minutes. We used the full spectrum. \xxx{...}

Concerning our SPOT maps: a gaussian prior with unit mean is a pretty bad prior for the spectrum.
In a more realistic scenario, we'd know a lot more information about the spectrum---such as where the lines are and some estimate of their shapes and depths---so the fidelity of our maps would be higher. This is what we did in the Luhman 16B case, and it works well. \xxx{...}

\subsection{Priors and regularization}
\label{sec:discussion:priors}
Discuss: how to choose priors. Can use cross-validation to choose best regularization strength. In general, a positivity prior on the pixels is preferred.
\xxx{...}

\subsection{Posterior sampling}
\label{sec:discussion:mcmc}

Discuss the case where the inclination/period/velocity is unknown, such as the case with Luhman 16B.
The problem is not linear in these variables, so we need MCMC. 
But our model is differentiable, so we can easily use HMC. 
Discuss.
\xxx{...}

\subsection{Limitations and future work}
\label{sec:discussion:caveats}

We are not addressing differential rotation and convective blueshift.
These make the integral in Equation~(\ref{eq:deconv:kT}) very difficult to solve. 
We will tackle this in the next paper.
\xxx{...}

The instrumental profile is another Toeplitz matrix that can be dotted into Equation~(\ref{eq:linear:f}).
\xxx{...}

We are always integrating over the entire disk of the star. Can integrate over the unocculted disk during an occultation (should actually be pretty trivial) so this can be used for Doppler tomography once I have some time to work it out!
\xxx{...}

Telluric lines could be learned from the data as in \citet{Bedell2019}.
\xxx{...}
